Título\\

### 2018-08-09 paper/paper.tex

% spanish symbols for narrative
\usepackage[utf8]{inputenc} 
% language
\usepackage[spanish]{babel}

%changing from roman number to integers
\renewcommand{\thesection}{\arabic{section}}
\renewcommand{\thesubsection}{\arabic{section}.\arabic{subsection}}

\usepackage{pgfplots}
\usepackage{pgfplotstable}
    \pgfplotsset{
        % use this `compat' level or higher to position the bars in one group
        % next to each other
        compat=1.7,
    }
    % load the data table ...
    \pgfplotstableread[col sep=comma]{femaleAgeDistribution.csv}{\femaleAgeDistribution}
        % and store the number of columns in `\NoOfCols'
        % (minus 1 because counting in `\foreach' starts with zero
        \pgfplotstablegetcolsof{\femaleAgeDistribution}
        \pgfmathtruncatemacro{\NoOfCols}{\pgfplotsretval-1}

@@

\title{Título\\
}

\author{\IEEEauthorblockN{Autores}
\IEEEauthorblockA{
\textit{Grupo de Investigación de Aprendizaje Profundo} \\
\textit{Departamento Ingeniería en Sistemas de Información}\\
\textit{Universidad Tecnológica Nacional}\\
\textit{Facultad Regional Rosario}\\
mail@frro.utn.edu.ar} %should be hyperlink
}

@@

% used PGFPlots v1.14

\begin{tikzpicture}
    \begin{semilogyaxis}[
        % adjust the `width' a bit by keeping the default `height'
        width=1.05*\axisdefaultwidth,
        height=\axisdefaultheight,
        % set appropriate `ymax' value so the `nodes near coords' fit to the plot
        % (adjusting the `ymin' value is just to make it look a little bit better)
        ymin=0,
        ymax=2000,
        % there should be no gap between the bars in one group
        ybar=0pt,
        % use data from the table for the xticklabels
        xtick=data,
        xticklabels from table={\femaleAgeDistribution}{Anio},
        % adjust the size of the bars so they don't overlap
        % (you can play with the numerator to change the gap between the groups)
        bar width=0.6/\NoOfCols,
        % enlarge the x limits so all of the bars are shown
        % (play with the value to adjust the gap on the sides of the plot)
        enlarge x limits={abs=0.6},
        % and position the legend outside of the plot to not overlap with the data
        %legend pos=outer north east,
        % add `nodes near coords'
        nodes near coords={
            % because internally PGFPlots works with floating point numbers, we
            % change them to fixed point numbers
            \pgfkeys{
                /pgf/fpu=true,
                /pgf/fpu/output format=fixed,
            }
            % truncate value count to integer
            \pgfmathparse{\pgfplotspointmeta}
            \pgfmathprintnumber{\pgfmathresult}\,
        },
        % set the style of the `nodes near coords'
        nodes near coords style={
            font=\tiny,
            rotate=90,
            anchor=west,
        },
        % as basis for the `nodes near coords' use the raw y values
        point meta=rawy,
    ]
        % add the data rows for each column 
        \foreach \i in {1,...,\NoOfCols} {
            \addplot table [
                x expr=\coordindex,
                y index=\i,
                col sep=comma,
            ] {\femaleAgeDistribution};
                % to automatically add the legend entries first extract the
                % column name and store it in `\colname'
                    \pgfplotstablegetcolumnnamebyindex{\i}\of{\femaleAgeDistribution}\to{\colname}
                % now you can add the legend entry
                % (because we are in a loop we have to use the "expanded" version)
                \addlegendentryexpanded{\colname};
        }
    \end{semilogyaxis}
\end{tikzpicture}

>>>>

\usepackage[utf8]{inputenc} % Acentos, etc
\usepackage[spanish]{babel} % Idioma

\renewcommand{\thesection}{\arabic{section}} %Se cambia de números romanos a número
\renewcommand{\thesubsection}{\arabic{section}.\arabic{subsection}} %Se cambia de %números romanos a número

@@

\title{Título\\
%{\footnotesize \textsuperscript{*}Note: Sub-titles are not captured in Xplore and
%should not be used}
%\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{Autores}
\IEEEauthorblockA{
\textit{Grupo de Investigación de Aprendizaje Profundo} \\
\textit{Departamento Ingeniería en Sistemas de Información}\\
\textit{Universidad Tecnológica Nacional}\\
\textit{Facultad Regional Rosario}\\
mail@frro.utn.edu.ar} %hacerlo hyperlink
}

@@
